|

### 2020-04-28 nontex/install/linux/fn_ubuntu.Rmd
over and unber bar, bold or not. bm mand accents package.

```{bash}
# install git
sudo apt-get install git
# generate repo directory and sync
mkdir ~/PyFan
# mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching
cd ~/PyFan
git init
# git config only needs to happen once, info stored under ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
git remote add github git@github.com:FanWangEcon/PyFan.git
git pull github master
```

@@

# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc

@@

```{r}
conda install -y statsmodels datashape seaborn
# conda install statsmodels
# conda install datashape
# conda install seaborn

conda install -c conda-forge -y interpolation awscli
# conda install -c conda-forge interpolation
# conda install -c conda-forge awscli

conda install -c anaconda -y boto3

# conda install -c r r-irkernel
```

>>>>

```{bash}
# install git
sudo apt-get install git
# generate repo directory and sync
mkdir ~/base
# mkdir fanwangecon.github.io base Tex4Econ R4Econ M4Econ Py4Econ Teaching
cd ~/base
git init
# git config only needs to happen once, info stored under ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
git remote add github git@github.com:FanWangEcon/base.git
git pull github master
```

@@

# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2020.02-Linux-x86_64.sh
# install file
bash "Anaconda3-2020.02-Linux-x86_64.sh"
# refresh
source ~/.bashrc

@@

```{r}
# Install poetry 
curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
# Install pyecon pyfan
pip install pyfan

# conda install -y statsmodels datashape seaborn
# conda install statsmodels
# conda install datashape
# conda install seaborn

# conda install -c conda-forge -y interpolation awscli
# conda install -c conda-forge interpolation
# conda install -c conda-forge awscli

# conda install -c anaconda -y boto3
# conda install -c r r-irkernel
```

### 2020-04-28 nontex/install/windows/fn_installations.Rmd
over and unber bar, bold or not. bm mand accents package.

1. Python (Anaconda, Pycharm + VSCode + Atom)
2. R (VSCode + Atom)
3. Matlab
4. Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)

@@

Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment. Push to github and Pypi, and then install via pip for system wide use.

@@

1. If a module requires another dependency: *poetry add numpy*, if adding numpy. This will install in the virtual env *numpy*.
2. Type in *poetry env info*, and copy path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env. 
    + in Pycharm: Settings (ctrl+alt+s) > Project > Python interpreter > click on the cog, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
3. When finished, *build* and *publish*

```{bash}
rm -rf dist/ build/
poetry install
poetry build 
poetry publish
# provide pypi username and password
```

## Local Install

```{bash}
pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/fantools-0.0.0.900.tar.gz" fantools --ignore-installed
```

## Pypi Install

@@

```{bash}
pip install git+https://github.com/fanwangecon/Py4Econ.git#egg=fantools

pip install fantools --ignore-installed
pip show fantools
```

```{python}
import fantools as fantools

@@

## First Time Conda Install

@@

###############################
# Add these to Windows PATH:
###############################
# C:\ProgramData\Anaconda3\Scripts
# C:\ProgramData\Anaconda3
```

To Add Anaconda to Path, In Windows
1. Search for: Environment Variables
2. Edit Environment Variables
3. Add new to Path (lower half):
    - C:/ProgramData/Anaconda3/Scripts/
    - C:/ProgramData/Anaconda3/
4. Now open up regular windows command Prompt, Type in:
    - conda --version
    - also Close and Open up Git Bash: conda --version

## Conda Update

@@

```{bash}
# if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all

# install additional packages
# linux utilites
conda install -y m2-base 
# stats and graphs
conda install -y statsmodels datashape seaborn
# various
conda install -c conda-forge -y interpolation awscli
# aws communicate
conda install -c anaconda -y boto3
```

## Install Packages

Note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.

@@

## Python Command Line Test

Fist test python under command line:

@@

- 7-zip
- evernote

>>>>

1. Python (Anaconda, Pycharm + VSCode + Atom, Poetry)
2. R (VSCode + Atom)
3. Matlab
4. Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)

@@

When to use Python:

1. Main use Python for Dynamic programing type tasks
2. All immediate data tasks should be done in R, including things like generating data structures. Also graph generation in R.
3. Certain basic tabulation summary statistics etc things done in Stata

Two types of python usage cases:

1. Small chunks of python code in RMD for tutorial/class files, combine files in book format as bookdown.
2. Python installable packages and modules created with poetry, push to github as pypi: Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment. Push to github and Pypi, and then install via pip for system wide use.

Installations:

1. Python package development in poetry virtual environment, install with needed dependencies.
	- This means, during python package development, do not install the packages needed directly in conda, but add as dependency in Poetry
2. General environment with pip installed packages and conda installed path discoverable pathon packages for rmd chunks.

@@

Install Python via Anaconda first following other instructions. Possibly cleanly uninstall and reinstall. Use Poetry to build python packages and modules.

For development machines, install [Poetry](https://github.com/python-poetry/poetry) and nstall [sphinx](https://www.sphinx-doc.org/en/master/).

```{bash}
# poetry
curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
# sphinx
pip install sphinx
```

Initialize a Poetry-style Python Package and add Sphinx style docs. This creates the folder *~/pyfan* and initialize it with various:

```{bash}
# creates ~/pyfan as poetry packaging
cd ~
poetry new pyfan

# sphinix quickstart
cd ~/pyfan
mkdir docs
sphinx-quickstart
make html

# build empty package
rm -rf dist/ build/
poetry install
poetry build
poetry publish

# What is the virtual Env id
poetry env info
```

### Installating Poetry Created Packages

Normally install/test/use inside conda virtual env or poetry virtual env. Poetry would install with *poetry add* and *poetry install*. After seeing some package of interest on github etc, see if the package is on pypi. pip install from pypi if possible.

Local Install

```{bash}
pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/pyfan-0.0.0.900.tar.gz" pyfan --ignore-installed
```

Pypi Install

@@

```{bash}
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
pip install pyfan --ignore-installed
pip show pyfan
```

Sometimes, someone ports a package and adds certain things that I need, so need to install from git a package whose modified version is not on pypi, then use git+https

#### What are egg, tar.gz, whl?

poetry creates tar.gz and whl in the dist folder, what are they?

- tarballs: tar.gz

### Developing and testing new tools Pycharm + Poetry

When tesing and developing tools, do so in the poetry virtual environment for the package in which testing is taking place.

After a package has been created and poetry built and poetry publish:

1. Type in *poetry env info*, and copy for example path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env.
2. In Pycharm: Settings (ctrl+alt+s), Project, Python interpreter.
3. Click on the cog button, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts

```{bash}
poetry env info
```

When a particular tool is needed to build this new module inside package, add the tool via poetry add as a dependency. If a module requires another dependency: *poetry add numpy*, if adding numpy. This will install in the virtual env *numpy*. When packages are added, they are automatically installed. When the the *pyfan* package repo is downloaded somewhere, the dependencies might not be installed yet, and *poetry install* would install them.

```{bash}
poetry add numpy
```

#### Development for pyfan

pyfan is the general python tools package for various projects, not economics related directly.

Poetry added dependencies are in */pyfan/pyproject.toml*, Poetry add:

```{bash}
cd "C:/Users/fan/pyfan"
cd ~/pyfan
poetry env info
```

All installations:

```{bash}
poetry remove python-frontmatter pyyaml
poetry add python-frontmatter pyyaml
```

Poetry modules added over time:

```{bash}
# 2020-04
poetry add pyyaml
poetry add python-frontmatter
```

After modules are added and new programs developed

```{bash}
cd ~/pyfan
cd "C:/Users/fan/pyfan"
poetry install
make html
rm -rf dist/ build/
poetry build
poetry publish
```

On some local computer install pyfan:

```{bash}
pip show pyfan
# conda activate pyfan
pip install pyfan
```

##### Uninstall

uninstall packages in the overall environment
```{bash}
# list all installed packages
pip list
pip show pyyaml
pip show python-frontmatter
pip show pyfan
# unstall packages
pip uninstall pyyaml
pip uninstall python-frontmatter
```

@@

## Anaconda Install

### First Time Conda Install

@@

###############################
# Add these to Windows PATH:
###############################
# C:\ProgramData\Anaconda3
# C:\ProgramData\Anaconda3\Scripts
# C:\ProgramData\Anaconda3\Scripts\bin
```

To Add Anaconda to Path, In Windows
1. Search for: Environment Variables
2. Edit Environment Variables
3. Add new to Path (lower half):
    - C:/ProgramData/Anaconda3/
    - C:/ProgramData/Anaconda3/Scripts/
    - C:/ProgramData/Anaconda3/Scripts/bin        
4. Now open up regular windows command Prompt, Type in:
    - conda --version
    - also Close and Open up Git Bash: conda --version

### Conda Update, Install, Channels

@@

```{bash}
# if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all
```

### Conda Environments

For testing installed packages. Note that for development, using poetry for testing package dependencies for package development, and associate pycharm for projects with poetry virtual environments. The idea is that there might be dependency problems etc for packages depending on where/when they were made, might not work in the overall conda environment where pyfan and pyecon, my main tools are installed. Some specific task might only need one particular package. And when working on these, use a conda environment. When this works, could incorporate whatever I am working on into a pyfan, pyecon package along with other packages.

```{bash}
conda list env
conda env remove -n test_package_name
conda create -n test_package_name -y
conda activate test_package_name
conda list
conda deactivate

conda install pip

# see if package exists on pip and install from pip
pip install smop
```

#### Conda Perl Environment

To run some perl tools in an isolated environment:

1. [latexpand](https://tex.stackexchange.com/a/21840/109818)

```{bash}
# Set up
conda list env
conda env remove -n wk_perl
conda create -n wk_perl -y
conda activate wk_perl
conda install -c anaconda perl
conda list
conda deactivate

# intall packages in virtual env
cd "C:\Users\fan\.conda\envs\wk_perl\"
git clone https://gitlab.com/latexpand/latexpand.git

# use latexpand
conda activate wk_perl
cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_edcc_submit_rr.tex > draft_edcc_submit_rr_flat.tex
```

#### Conda Jinja Environment

For testing and packaging latex files. In particular, single folder latex files for final paper submissions.

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_jinja
conda create -n wk_jinja -y
conda activate wk_jinja
conda install -c anaconda jinja2
conda install -c anaconda pyyaml

# use yaml2tex
cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
python yaml2tex.py
```

## Essential Programs to Install

Install Packages, note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.

@@

Previously:

```{bash}
# install additional packages
# linux utilites
# conda install -y m2-base
# stats and graphs
# conda install -y statsmodels datashape seaborn
# various
# conda install -c conda-forge -y interpolation awscli
# aws communicate
# conda install -c anaconda -y boto3
```

## Fist test python under command line:

@@

- [pandoc](https://pandoc.org/installing.html)
- 7-zip
- evernote
